### 2015-02-19 fundamentals/fcsreqs.tex
the genius acronym should just encapsulate the acronym.
cleanup, fcsreqs

Many fuel cycle phenomena have aggregate system-level effects which can only be
captured by discrete material tracking \cite{huff_next_2010}.  \Cyclus
tracks materials as discrete objects. Some current fuel cycle simulation tools
such as \gls{COSI}
\cite{mccarthy_benchmark_2012,grasso_nea-wpfc/fcts_2009,guerin_benchmark_2009},
\gls{DESAE}
\cite{andrianova_desae_2008}, FAMILY21\cite{mccarthy_benchmark_2012},
\gls{GENIUSv1}, \gls{GENIUSv2}, and \gls{NFCSim} also possess the ability to
model discrete materials.

Similarly, the ability to model disruptions (i.e. facility shutdowns due to
insufficient feed material or insufficient processing and storage capacity) is
most readily captured by software capable of tracking the operations status of
discrete facilities \cite{huff_next_2010}.  Fleet-based models (i.e.
\gls{VISION}) are unable to capture this gracefully.  All of the software
capable of discrete materials have a notion of discrete facilities, however not
all handle disruption in the same manner. \gls{DESAE}, for example, does not
allow shutdown due to insufficient feedstock, though \Cyclus does. In the event
of insufficient fissile material during reprocessing, \gls{DESAE} borrows
material from storage, leaving a negative value \cite{mccarthy_benchmark_2012}.

@@

In addition to being inaccessible, the vast majority of fuel cycle simulators
are, effectively, inextensible. Typical fuel cycle simulator development teams are insular, in
part due to accessibility issues. Also, however, their frameworks contain
heuristics and assumptions that constrain developer additions.

For example, where most other simulators describe a finite set of acceptable
cycle constructions (once through, single-pass, multi-pass), the \Cyclus
simulation logic relies on a market paradigm that can be easily directed to
create novel material and economic paths. The simulation of the dynamic
responses within the system to pricing, availability, and other institutional
preferences in \Cyclus is an advanced capability and does not exist in a
flexible manner for other fuel cycle simulators.

>>>>

Many fuel cycle phenomena have aggregate system-level effects which can only be
captured by discrete material tracking \cite{huff_next_2010}.  \Cyclus
tracks materials as discrete objects. Some current fuel cycle simulation tools
such as \gls{COSI}
\cite{mccarthy_benchmark_2012,grasso_nea-wpfc/fcts_2009,guerin_benchmark_2009},
\gls{DESAE}
\cite{andrianova_desae_2008}, FAMILY21\cite{mccarthy_benchmark_2012},
\gls{GENIUS} version 1, \gls{GENIUS} version 2, and \gls{NFCSim} also possess the ability to
model discrete materials.

Similarly, the ability to model disruptions (i.e. facility shutdowns due to
insufficient feed material or insufficient processing and storage capacity) is
most readily captured by software capable of tracking the operations status of
discrete facilities \cite{huff_next_2010}.  Fleet-based models (i.e.
\gls{VISION}) are unable to capture this gracefully.  All of the software
capable of discrete materials have a notion of discrete facilities, however not
all handle disruption in the same manner. \gls{DESAE}, for example, does not
allow shutdown due to insufficient feedstock. In the event
of insufficient fissile material during reprocessing, \gls{DESAE} borrows
material from storage, leaving a negative value \cite{mccarthy_benchmark_2012}.
The \Cyclus framework does not dictate such heuristics. Rather, it provides a
flexible framework on which either method is possible.

@@

In addition to being inaccessible, the vast majority of fuel cycle simulators
are, effectively, inextensible. Typical fuel cycle simulator development teams are insular, in
part due to aforementioned accessibility issues. Accordingly, their frameworks
typically contain heuristics and assumptions that constrain developer additions.

For example, most current simulators describe a finite set of acceptable
cycle constructions (once through, single-pass, multi-pass). That limits the
capability to create novel material flows and economic scenarios. The \Cyclus
simulation logic relies on a market paradigm, parameterized by the user, which
flexibly simulates dynamic responses to pricing, availability, and other
institutional preferences. This is an advanced level of flexibility that does
not exist in other fuel cycle simulators.

### 2015-02-19 fundamentals/impl.tex
cleanup, fcsreqs

Although some questions require resolution at the level of
individual facilities and materials,
Fleet-based, lumped-material models do not distinguish between discrete
facility entities or materials.  As a result, many detailed performance
metrics cannot be captured with previously existing tools.
The generality of \Cyclus therefore enables many use cases
that cannot be achieved with fleet-based models.

@@

\TODO{AO Opinion: Move some of the detail from this intro to the main section
on discrete materials. Then add an intro to the discrete time/DRE as well.}

>>>>

Fleet-based, lumped-material models do not distinguish between discrete
facility entities or materials. However, some questions require resolution at the level of
individual facilities and materials.
As a result, many detailed performance
metrics cannot be captured with previously existing fleet-based models.

@@

### 2015-02-19 fundamentals/intro.tex
cleanup, fcsreqs

\Cyclus, therefore, is a dynamic, agent-based model, which employs a modular
architecture, an open development process, discrete agents, discrete time, and
arbitrarily detailed isotopic resolution of materials. Dynamic nuclear fuel
cycle analysis more realistically supports a range of simulation goals than
static analysis \cite{piet_dynamic_2011}. Similarly, experience in the broader
field of systems analysis indicates that agent-based modeling enables more
flexible simulation control, without loss of generality
\cite{macal_agent-based_2010}. Finally, openness allows cross-institutional
collaboration, increases software robustness \cite{cohen_modern_2010}, and
cultivates an ecosystem of modeling and calculation options.  Comprising
flexible, interchangeable models of fuel cycle components with varying scope,
depth and fidelity, this ecosystem allows users and developers to customise
\Cyclus to analyze the cases that are of interest to them, rather than those
the simulator was originally developed to address.  The fundamental concepts of
the \Cyclus nuclear fuel cycle simulator capture these modern insights so that
challenges in nuclear fuel cycle analysis can be better addressed.

@@

However, methods for calculating those metrics vary among simulators. Some
model the system of facilities, economics, and materials in static equilibrium,
while other simulators capture the dynamics of the system.  Similarly, while
some simulators discretely model batches of material and individual facilities,
others aggregate facilities into fleets and materials into streams. Simulators
can model a single aspect of the fuel cycle in great detail while neglecting
others. For example, a simulator created for policy modeling might have
excellent capability in economics while models affecting transformations in
material isotopics or the effects of isotopics on technology performance are
neglected.  The \gls{CAFCA}\cite{guerin_impact_2009} simulator is problem-oriented
in this way.

>>>>

\Cyclus, therefore, is a dynamic, agent-based model, which employs a modular
architecture, an open development process, discrete agents, discrete time, and
arbitrarily detailed isotopic resolution of materials. Dynamic nuclear fuel
cycle analysis more realistically supports a range of simulation goals than
static analysis \cite{piet_dynamic_2011}. Similarly, experience in the broader
field of systems analysis indicates that agent-based modeling enables more
flexible simulation control, without loss of generality
\cite{macal_agent-based_2010}. Finally, openness allows cross-institutional
collaboration, increases software robustness \cite{cohen_modern_2010}, and
cultivates an ecosystem of modeling and calculation options. Comprised of
flexible, interchangeable models of fuel cycle components with varying scope,
depth and fidelity, this ecosystem allows users and developers to customise
\Cyclus to analyze the cases that are of interest to them, rather than those
the simulator was originally developed to address.  The fundamental concepts of
the \Cyclus nuclear fuel cycle simulator capture these modern insights so that
novel challenges in nuclear fuel cycle analysis can be better addressed.

@@

However, methods for calculating those metrics vary among simulators. Some
model the system of facilities, economics, and materials in static equilibrium,
while other simulators capture the dynamics of the system.  Similarly, while
some simulators discretely model batches of material and individual facilities,
others aggregate facilities into fleets and materials into streams. Simulators
can model a single aspect of the fuel cycle in great detail while neglecting
others. For example, a simulator created for policy modeling might have
excellent capability in economics while capabailities for tracking transformations in
material isotopics and the effects of isotopics on technology performance are
neglected.  The \gls{CAFCA}\cite{guerin_impact_2009} simulator is problem-oriented
in this way, having elected to neglect isotopic resolution in favor of
integral effects.
